Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach

### 2016-05-07 sections0.01/results0.01.tex
Applied Pauline's and Hossein's result. Result0.01 is grammatically corrected (~ish)

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{RESULTS and DISCUSSION}
\label{sec: result}
    In this section we are showing the results of trained neural networks, using K96 data. 
    To have a realistic model of the input data we created SOMs with various sizes in both 1D and 2D.
    We start our analysing by creating 1D SOMs. 
    First, we created SOMs with only two neurons (1$\times$2 map) and then we increased number of neurons one at a time in 1D case (~\ref{sec: 1D}).
    Then we generated 2D networks (~\ref{sec: 2D}), and once again we start with smallest number of neuron possible (4 neurons in 2$\times$2 map) and then increased the number of neurons to 144 in 12$\times$12 map.

    For each generated network, we compare the results with K96 categorization.
    We also used these networks to classify the T12 galaxies samples, and compare them with classifications from supervised network.
    \subsection{1D SOMs}
    \label{sec: 1D}
        \subsubsection{TRAINING THE NETWORKS}
        \label{sec: 1Dt}
            We assumed that galaxies can be divided only in two types; quiescent and star burst, and then generated a network with only two neurons.
            Then we increased size of the maps gradually till we separated the input 12 sample galaxies into the 12 neurons.

            Figs.~\ref{fig: 1by2T} -~\ref{fig: 1by3T} show results of training network.
            Upper part of the figures shows neurons and their relative distances ($D_j$) from each other.
            As it was mentioned in the Sec.~\ref{sec: method}, the colours between neurons represents the relative distance $D_j$ between the neurons and the darker is the colour the more $D_j$ is between them.
            The lower part shows how many galaxies from K96 template places in each neurons.

            In upper side of the Fig.~\ref{fig: 1by2T}, the red colour between two neurons indicate that the $D_j$ between these two groups are relatively high, and these two groups are distinguishable groups.
            In the lower part of the Fig.~\ref{fig: 1by2T}, we see galaxies divided to two groups of 5 and 7.
            Although we know from K96 and T12 that 6 of the galaxies are quiescent and the other 6 are star bursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
            In this method, the Sc galaxies have been categorized as star burst galaxy due to their high amount of the emission lines.

            %add more about why Sc is acting differently
            %\import{~/images/texes/}{1by2_t.tex}
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by2T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by2Thits}
                \end{subfigure}
                \caption{Results of training network in $1\times2$~grid. In this network, 5 of galaxies from K96 model, categorized as quiescent galaxies and the rest are star bursts. Because of their high emission lines, Sc galaxies moved towards the star burst ones.}
                 \label{fig: 1by2T}
            \end{figure}

            Fig.~\ref{fig: 1by3T} shows results of the training in a 1$\times$3 network.
            In these plots we forced the galaxies to categorized themselves in maximum 3 groups. 
            If the galaxies in Fig.~\ref{fig: 1by2T} are very similar to each other or are exactly the same, they still want to be divided in two groups and left the middle node empty. 
            However, in the lower part of the Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two galaxies.
            These two galaxies, which are separated from group of star bust galaxies in the lower part of Fig.~\ref{fig: 1by2T},are types SB5 and SB6 galaxies.
            In upper plot of the Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is yellow. 
            The black colours indicates that the left neuron is completely different from the other two groups, while the yellow colour shows the two neurons are very similar to one another.

            Comparing Fig.~\ref{fig: 1by2T} with Fig.~\ref{fig: 1by3T} shows us that the star burst galaxies are divided to two groups. 
            Based on the colours between these two groups, we conclude that they are very similar groups; both groups are star burst galaxies and have strong emission lines.
            However, these two groups have the most internal colour extinctions, so they intend to move more towards the early type galaxies.

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_3.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_3.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Results of training network in $1\times3$~grid. In this network again, 5 of galaxies from K96 model, categorized as quiescent galaxies, and 7 as star bursts. However, this time 2 of galaxies (SB5, and SB6) are separated star bursts groups.}
                 \label{fig: 1by3T}
            \end{figure}

            We increased the size of maps gradually till the galaxies were divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} and ~\ref{fig: 1by22T}).
            Since there are more nodes when with increasing the size of map, program pays more attention to small differences between each groups.
            Higher the size of the maps means that even considering the smallest differences between galaxies.
            If the galaxies from K96 had completely different and distinct SED, SOM with size of $1\times12$ were expected to show 12 different groups of galaxies (1 each node).
            However, in Fig.~\ref{fig: 1by12T}, we see that three of neurons contains two galaxies and  three of them are empty. 
            In Fig.~\ref{fig: 1by12T} from left to right galaxies with types of B and E, SB3 and SB4, and SB1 and SB2, are the ones groups together, respectively. 
            The SB3 and SB4 grouping breaks when we increased the size of the map to $1\times15$~(Fig.~\ref{fig: 1by15T}).
            The SB1 and SB2 galaxies remained in the same neurons till we increased the size of map to $1\times20$~(Fig.~\ref{fig: 1by20T}), and the separation between galaxies B and E does not happened before the size of the SOM reached to $1\times22$~(Fig.~\ref{fig: 1by22T}).
        \begin{figure*}
            \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_22.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_22.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
            \end{subfigure}
            \caption{Results of training network in $1\times22$~grid.}
            \label{fig: 1by22T}
        \end{figure*}

            In Fig.~\ref{fig: 1by22T}, although in lower plot we can see twelve different groups, but in upper plot 5 groups are in the left side neurons and there is a black colour between them and then the rest of the galaxies. 
            It shows that although we separated the galaxies in twelve groups but they are still divided by two main groups.
            The closest occupied neurons in the star burst side of the SOM, belongs to the SB6 type. 
            This type of the galaxies have the most extinction and its SED has similarity to early type galaxies more than other star burst types.

            The fact that the galaxies had to have 22 different neurons till be divided to 12 groups, shows that the difference between SB1 and SB2, and B and E galaxies are very small.
            These small differences might be very hard to distinguish in normal classification methods and might lead to wrong classifications.

        \subsubsection{ CLASSIFYING SAMPLE OF GALAXIES}
         \label{sec: 1Dv}
            We used each network that we trained in Sec.~\ref{sec: 1Dt}, to classifying the sample 142 galaxies from T12.
            Upper plot in the Fig.~\ref{fig: 1by2V} shows the result of the classifying of the T12 galaxies using the $1 \times 2$~network from Fig.~\ref{fig: 1by2T}.
            It shows that 80 of the galaxies have SEDs similar to the early type galaxies and the SEDs of the rest of them are similar to star burst galaxies.
            The lower plot shows the average SED of the SEDs galaxies in each node. 
            The left plot shows the average SED of 80 galaxies that classify as an early type galaxies. 
            These are the similar ones sit on the left node in the upper plot in the Fig.~\ref{fig: 1by2T}.
            The plots clearly shows the 4000\AA~break in the SEDs, which is the one of the signatures of the SED of the early type galaxies.
            The strong the emission line in that figure comes from the galaxies with similar SED to Sa galaxies but with more strong emission lines.
            The right plot in the lower part of the Fig.~\ref{fig: 1by2V} shows strong emission lines and high emissions in the lower wavelengths, which are the signs of the strong star formation in the galaxies. 
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images/1d/SED_total1by2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Classifying galaxies from T12, based on their SEDs using $1\times2$~networks that were trained from 12 galaxies from K96. Up: Numbers in each node represents the number of galaxies that belong to that group. In this case 80 means that 80 of the 142 galaxies classify as the early type groups while the 62 of the 142 galaxies categorize to the star burst galaxies. Down: Average SED of the SEDs of the galaxies in each group. the left plot shows the average SED of the 80 galaxies (early type ones), and the right plot shows the average SED of the SEDs of 62 galaxies (star burst ones).}
                \label{fig: 1by2V}
            \end{figure}            
            Since in this network galaxies forced to divided to two groups, for any SED between these two groups the SOM decides that the galaxy belongs to which group based on the strongest features of its SED.
            The galaxies with a weak 4000\AA~break but strong emission lines and increase of the flux in the lower wavelengths categorized as star bursts while galaxies with strong 4000\AA~break, but high emission lines categorized as the early type.
            Increasing the size of the SOM helps to solve problem of the galaxies which have features of both groups.

             Fig.~\ref{fig: 1by3V} represents the result of the classifying the SED of the galaxies using the $1\times3$~network ( Fig.~\ref{fig: 1by2T}). 
             In the upper plot of this figure we can see 66 of the galaxies belongs to the early type group, and 47 belong to star burst galaxies. 
             29 of the galaxies are more similar to star burst ones but, not with all of their features. 
             These group of galaxies have strong emission lines and the ascending slop towards the lower wavelengths, but they also have a strong 4000\AA~break, which makes them to move towards the early type galaxies (middle plot in the lower part of the Fig.~\ref{fig: 1by2V}).

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_3.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/SED_total1by3.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Same as Fig.~\ref{fig: 1by2V}, but this time we used network with size of $1\times3$ to classify the sample galaxies.}
                \label{fig: 1by3V}
            \end{figure}

            In Fig.~\ref{fig: 1by22V}, we used the $1\times22$~network to classify the the sample galaxies.
            As mentioned in the Sec.~\ref{sec: 1Dt}, this network size is the first size we could see, the K96 galaxies separated in 12 different neurons.
            B and E or SB1 and SB2 galaxies were too similar to SOM can recognize them as two separate groups.
            The same as Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, upper plot of the Fig.~\ref{fig: 1by22V} shows how many of galaxies from the 142 galaxies, moved to each neuron in the $1\times22$ SOM.
            \begin{figure*}
                \begin{subfigure}[b]{0.9\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_22.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.9\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/SED_total1by22.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Same as Fig.~\ref{fig: 1by2V}, but this time we used network with size of $1\times22$ to classify the sample galaxies.}
                \label{fig: 1by22V}
            \end{figure*}
            And the lower plot of the figure represents the average SED of the galaxies in each neurons.
            However, this time, since galaxies had more space to separated some of the neurons left empty. 
            Thus instead of having 22 average SED plots in the lower part of the Fig.~\ref{fig: 1by22V}, we have 12 SEDs.

            By comparing the upper part of Fig.~\ref{fig: 1by22V} with the lower part of the Fig.~\ref{fig: 1by22T}, we can see that the occupied neurons are not necessarily the same.
            If a groups of the T12 galaxies fills the same neurons as a K96 galaxies, we can conclude that this group of the galaxies have SEDs very similar to the SED of one of K96 galaxies.
            Whereas, we can conclude that a group of the galaxies have properties between the two groups if they fill a neuron which is empty and places between two categories of galaxies in the Fig.~\ref{fig: 1by22T}.
            However, the colours between these neurons in the upper side of the Fig.~\ref{fig: 1by22T}, establishes that the group of galaxies are more similar to which group.

            In the first two neurons of the upper plot in the Fig.~\ref{fig: 1by22V}, there is no galaxies, while in galaxies B and E are in the same neurons in the trained network.
            So we can conclude that there is no galaxies with similar
            There are 3 galaxies in the third neurons which shows these 3 galaxies are very much similar to the S0 type. 
            18 of the galaxies are on the fifth neurons and similar to the Sa type of the galaxies, while the 7 galaxies in the fourth neurons have SEDs similar to both S0 and Sa galaxies.
            There is one Sb type galaxy and 15 galaxies with SED similar to both Sa and Sb type galaxies.
            The following two neurons (eighth and ninth neurons from the left) are in the edge of the early type and star burst galaxies.
            In the upper plot in the  Fig.~\ref{fig: 1by22T}, the colour between these two neurons are black, which indicates that the weights between these two are really different from each other.
            Therefore, 24 galaxies in the eighth neurons have similar SEDs to Sb type galaxies and SEDs of the 14 galaxies in the ninth neurons are similar to the SB6 galaxies.
            The far right of the network, galaxies with SED comparable to type SB1 and SB2.

            In general from the 142 galaxies in T12, we categorized them as following; three of the galaxies belongs to SO galaxies, fifteen are Sa, one is Sb, four are SB6, two are SB5, and 21 have a similar SED to SB2.
            The rest of the galaxies have SEDs in between of the initial 12 suggestions.
            As T12 mentioned, part of the reason we could not classify all the galaxies using the K96 model is that the model were constructed from co-adding 12 spectra of the 70 galaxies.
            In this small sample, it is quite possible that the best SEDs do not match any model, perfectly and the original classifications have high uncertainty.

            On the other hand, all the other methods (i.e. $\chi^2$ fitting, trained neural network) of matching SEDs limit themselves to models, and if they could not find the best match, report the results as an uncertain ones.
            However, with SOM, galaxies have this freedom to be categorized in the intermediate groups.
            Therefore, if the SED of galaxies do not match completely with any of the model SEDs in Fig.~\ref{fig: k96}, they can be categorized as a SED with similarity to two or more of the groups.

        \subsubsection{1D NETWORKS results and Properties of galaxies}
        In order to check weather our conclusions in Sec.~\ref{sec: 1Dv}~is meaningful and correct, we plot the some physical properties listed in the Tab.~\ref{tab: props} of galaxies in each neurons in the networks.

        \begin{figure*}
            \centering
            \includegraphics[width=\textwidth]{../images0.01/1d/props3.png}
            \caption{Comparing the median of four propertied of galaxies in each nod in $1\times2$, $1\times4$, and $1\times8$ networks.}
            \label{fig: props}
        \end{figure*}

        %         \begin{figure}
        %     \centering
        %     \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_3.png}
        %     \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by3V}}
        %     \label{fig: prop1by3}
        % \end{figure}

        %         \begin{figure}
        %     \centering
        %     \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_22.png}
        %     \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by22V}}
        %     \label{fig: prop1by22}
        % \end{figure}

        Fig.~\ref{fig: props} shows the results of median of stellar mass, age, specific star formation rate (SSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each nodes in the upper maps of the Figs.~\ref{fig: 1by2V} to ~\ref{fig: 1by22V}.
        In all the plots $x$-axis shows the number of the neurons from left to right, and $y$-axis shows one of the mentioned properties.

>>>>

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{RESULTS and DISCUSSION}
\label{sec: result}

    In this section we are showing the results of trained neural networks, using K96 data.
    Training networks with K96 templates, provides us networks that have regions with known morphological types. The trained networks can be used to categorize other galaxies.
    %In following we show how we trained data and used galaxies from T12 to show how the clustering using trained networks works.

    %%% should I move this paragraph to method section?!
    In order to find sufficient size for the trained networks, we created maps with sizes from $1\times2$ to $50\times50$.
    Varying grid of the maps helps us to monitor whether grouping galaxies in smaller maps is based on their similar SEDs or its for the shortage of the neurons.
    Based on size the data and SOM results, we chose maximum of the grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
    For each grid we created different SOMs with different learning factors, neighbourhood distances, and iteration numbers to find the optimum result for our sample.
    We created the final SOMs with following initial values: number of iterations in ordering phase = 1000; ordering phase learning factor = 0.9; tuning phase learning factor= 0.02; and tuning phase neighbourhood distance to be 1.

    We started our analysis by creating 1D SOMs. 
    First, we created SOMs with only two neurons ($1\times2$ map), and then we increased number of neurons one at a time in the 1D case (Sec.~\ref{sec: 1D}).
    We generated 2D networks (Sec.~\ref{sec: 2D}), and once again we start with the smallest number of neuron possible (4 neurons in $2\times2$ map), and then increased the number of neurons to 144 in $12\times12$ map.

    For each generated network, we compared the results with K96 categorization.
    We also used these networks to classify the T12 galaxies samples, and compared them with classifications from supervised networks in T12.
    \subsection{1D SOMs}
    \label{sec: 1D}
        \subsubsection{TRAINING THE NETWORKS}
        \label{sec: 1Dt}
            To start our clustering, we assumed that galaxies can be divided only in two types; quiescent and star burst.
            In this case, we generated a network with only two neurons.
            We increased the size of the map gradually till we separated the input 12 sample galaxies into the 12 neurons.

            Figs.~\ref{fig: 1by2T} -~\ref{fig: 1by22T} show results of training networks.
            Similar to Fig.~\ref{fig: sample}, the upper part of the figures shows neurons and their relative distances ($D_j$) from each other.
            As it was mentioned in the Sec.~\ref{sec: method}, the colours between neurons represents the relative distance, $D_j$, between the neurons and the darker is the colour the more $D_j$ is between them.
            The lower part shows how many galaxies from K96 template places in each neuron. 
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_2.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_2.png}
                \end{subfigure}
                \caption{Results of training network in $1\times2$~grid. Similar to Fig.~\ref{fig: sample} the upper plot is a distance map and the lower plot is a hit map. In this network, 5 of galaxies from K96 model, categorized as quiescent galaxies and the rest are star bursts. Because of their high emission lines, Sc galaxies moved towards the star burst ones.}
                 \label{fig: 1by2T}
            \end{figure}

            In the upper map in Fig.~\ref{fig: 1by2T}, the dark colour between two neurons indicates that the $D_j$ between these two groups are relatively high, and these two groups are distinguishable groups. 
            In the lower part of Fig.~\ref{fig: 1by2T}, we see galaxies divided to two groups of 5 and 7.
            Although we know from K96 and T12 that 6 of the galaxies are quiescent and the other 6 are star bursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
            In this method, the Sc galaxies have been categorized as star burst galaxy due to the relatively higher amount of the disk stellar population relative to the bulge ones. 
            According to K96, Sc galaxies are considered as late Hubble type galaxies which have more flat SED compare to other quiescent galaxies.

            Fig.~\ref{fig: 1by3T} shows the results of the training in a 1$\times$3 network.
            In these plots we forced the galaxies to categorize themselves in maximum 3 groups. 
            If the galaxies in Fig.~\ref{fig: 1by2T} were very similar to each other or were exactly the same, they still wanted to be divided into two groups and left the middle node empty. 
            However, in the lower part of Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two galaxies.
            These two galaxies, which are separated from group of star burst galaxies in the lower part of Fig.~\ref{fig: 1by2T}, belong to SB5 and SB6 types.
            In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
            The black colour indicates that the left neuron is completely different from the other two groups.
            While the white colour shows the two neurons are very similar to one another.

            Comparing Fig.~\ref{fig: 1by2T} with Fig.~\ref{fig: 1by3T} shows us that the star burst galaxies are divided into two groups. 
            Based on the colours between these two groups, we conclude that they are very similar groups; both groups are star burst galaxies and have strong emission lines.
            However, SB5 and SB6 types have the most internal extinctions.
            The high amount of extinction causes SED become more flat in the lower wavelength regions.
            The flatness in the UV part of the SED eventually makes these two types of galaxies become more similar to quiescent galaxies than other star burst ones.
            So in the networks, SB5 and SB6 types intend to move more towards the early type galaxies.

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_3.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_3.png}
                \end{subfigure}
                \caption{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times3$~grid. In this network again, 5 of galaxies from K96 model, categorized as quiescent galaxies, and 7 as star bursts. However, this time 2 of galaxies (SB5, and SB6) are separated star bursts groups.}
                 \label{fig: 1by3T}
            \end{figure}

            We increased the size of maps gradually till the galaxies were divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} and ~\ref{fig: 1by22T}).
            Since there are more nodes in higher grid SOMs, the program pays more attention to small differences between each group.
            Higher the size of the maps means that even considering the smallest differences between galaxies.
            If the galaxies from K96 had completely different and distinct SED, SOM with size of $1\times12$ were expected to show 12 different groups of galaxies (1 at each node).
            However, in Fig.~\ref{fig: 1by12T}, we see that three of neurons contains two galaxies and  three of them are empty. 
            In Fig.~\ref{fig: 1by12T} from left to right galaxies with types of B and E, SB3 and SB4, and SB1 and SB2, are the ones groups together. 
            The SB3 and SB4 grouping breaks when we increased the size of the network to $1\times15$~(Fig.~\ref{fig: 1by15T}).
            The SB1 and SB2 galaxies remained in the same neurons till we increased the size of map to $1\times20$~(Fig.~\ref{fig: 1by20T}), and the separation between galaxies B and E had not happened before the size of the SOM reached to $1\times22$~(Fig.~\ref{fig: 1by22T}).
        \begin{figure*}
            \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_22.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_22.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
            \end{subfigure}
            \caption{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times22$~grid.}
            \label{fig: 1by22T}
        \end{figure*} %PB160427: this figure looks really great! Very easy to understand.

            In Fig.~\ref{fig: 1by22T}, in lower plot we can see twelve different groups. 
            In upper plot 5 groups are in the left side neurons, and there are two dark grey colours between them and then the rest of the galaxies. 
            It shows that although we separated the galaxies in twelve groups, but they are still divided in two main groups.
            The closest occupied neurons in the star burst side of the SOM, belongs to the SB6 type. 
            This type of the galaxies has the most extinction and its SED has similarity to early type galaxies more than other star burst types.

            The fact that the galaxies had to have 22 different neurons till be divided into 12 groups, shows that the difference between SB1 and SB2, and B and E galaxies are very small.
            These small differences might be very small.
            Therefore, they intend to stay in the same group till the network become big enough to make attention to the smallest particularity.
           % For using SOM method, one should be careful about these small differences and consider that how much details do we need to pay attention to, to consider two groups are separate from each other.
           %%%% (I'm not sure if it is good to be here or not)
        \subsubsection{ CLASSIFYING SAMPLE OF GALAXIES}
         \label{sec: 1Dv}
            We used each network that we trained in Sec.~\ref{sec: 1Dt}, to classifying the sample 142 galaxies from T12.
            Upper plot in Fig.~\ref{fig: 1by2V} shows the result of the classifying of the T12 galaxies using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
            It shows that 80 of the galaxies have SEDs similar to the early type galaxies and the SEDs of the rest of them are similar to star burst galaxies.
            The lower plot shows the average SED of the galaxies in each node. 
            The left plot shows the average SED of 80 galaxies that classify as an early type galaxies. 
            These galaxies are similar to the ones in the left node in the upper plot in Fig.~\ref{fig: 1by2T}.
            The plots clearly show the 4000\AA~break in the SEDs, which is one of the signatures of the early type galaxies.
            The strong emission lines in that figure could be from the galaxies with similar SED to Sa galaxies but with more strong emission lines.
            The right plot in the lower part of Fig.~\ref{fig: 1by2V} shows strong emission lines and high emissions in the lower wavelengths, which are the signs of the strong star formation in the galaxies. 
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/SED_total1by2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Classifying galaxies from T12, based on their SEDs using $1\times2$~networks that were trained from 12 galaxies in Fig.~\ref{fig: 1by2T}. Up: the same as other hit maps, numbers in each node represents the number of galaxies that belong to that group. In this case 80 means that 80 of the 142 galaxies classify as the early type groups while the 62 of the 142 galaxies categorize to the star burst galaxies. Down: Average SED of the SEDs of the galaxies in each group. The left plot shows the average SED of the 80 galaxies (early type ones), and the right plot shows the average SED of the SEDs of 62 galaxies (the star burst ones).}
                \label{fig: 1by2V}
            \end{figure}            
            Since in this network galaxies forced to be divided into maximum two groups, for any SED between these two groups the SOM must decide that each galaxy belongs to which group based on strongest features of its SED.
            The galaxies with a weak 4000\AA~break but strong emission lines and increase of the flux in the lower wavelengths categorized as star bursts while galaxies with strong 4000\AA~break, but high emission lines categorized as the early type.
            Increasing the size of the SOM helps to solve the problem of the galaxies which have features of both groups.

             Fig.~\ref{fig: 1by3V} represents the result of the classifying the SED of the galaxies using the $1\times3$~network (from Fig.~\ref{fig: 1by2T}). 
             In the upper plot of this figure we can see 66 of the galaxies belongs to the early type group, and 47 belong to star burst galaxies. 
             29 of the galaxies are more similar to star burst ones, but not with all of their features. 
             These groups of galaxies have strong emission lines and the ascending slope towards the lower wavelengths, but they also have a strong 4000\AA~break, which makes them to move towards the early type galaxies (middle plot in the lower part of Fig.~\ref{fig: 1by2V}).

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_3.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/SED_total1by3.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used network with size of $1\times3$ (Fig.~\ref{fig: 1by3T}) to classify the sample galaxies.}
                \label{fig: 1by3V}
            \end{figure}

            In Fig.~\ref{fig: 1by22V}, we used the $1\times22$~network to classify the sample galaxies.
            As mentioned in the Sec.~\ref{sec: 1Dt}, this network size is the first size that we could see the K96 galaxies separated in 12 different neurons.
            B and E or SB1 and SB2 galaxies were too similar to SOM can recognize them as two separate groups.
            The same as Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, upper plot of Fig.~\ref{fig: 1by22V} shows how many of galaxies from the 142 galaxies, moved to each neuron in the $1\times22$ SOM.
            \begin{figure*}
                \begin{subfigure}[b]{0.9\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_22_n.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.9\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/SED_total1by22.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times22$ (Fig.~\ref{fig: 1by22T}) to classify the sample galaxies. In the average SED of each neuron, we can clearly see the changes from early type galaxies in the star burst ones. 4000\AA~ break reduces from left to right and emission lines increase.}
                \label{fig: 1by22V}
            \end{figure*}
            The lower plot of the figure represents the average SED of the galaxies in each neuron.
            However, this time, since galaxies had more space to separate some of the neurons left empty. 
            Thus, instead of having 22 average SED plots in the lower part of Fig.~\ref{fig: 1by22V}, we have 12 SEDs.

            By comparing the upper part of Fig.~\ref{fig: 1by22V} with the lower part of Fig.~\ref{fig: 1by22T}, we can see that the occupied neurons are not necessarily the same.
            If a group of the T12 galaxies fills the same neurons as the K96 galaxies, we can conclude that these galaxies have SEDs very similar to the SED of one of K96 galaxies.
            Whereas, we can conclude that a group of the galaxies has properties between the two groups if they fill a neuron which is empty and places between two categories of galaxies in Fig.~\ref{fig: 1by22T}.
            However, the colours between these neurons in the upper side of Fig.~\ref{fig: 1by22T}, establishes that those galaxies are more similar to which group.

            In the first two neurons of the upper plot in Fig.~\ref{fig: 1by22V}, there is no galaxy, while in galaxies B and E are in the same neurons in the trained network.
            So we can conclude that there is no galaxy with similar specification of type B or E in the T12 sample.
            There are 3 galaxies in the third neuron, which shows these 3 galaxies are very much similar to the S0 type. 
            18 of the galaxies are on the fifth neurons and similar to the Sa type of the galaxies, while the 7 galaxies in the fourth neurons have SEDs similar to both S0 and Sa galaxies.
            There is one Sb type galaxy and 15 galaxies with SED similar to both Sa and Sb type galaxies.
            The following two neurons (eighth and ninth neurons from the left) are on the edge of the early type and star burst galaxies.
            In the upper plot in the  Fig.~\ref{fig: 1by22T}, the colour between these two neurons are black, which indicates that the weights between these two are really different from each other.
            Therefore, 24 galaxies in the eighth neurons have similar SEDs to Sb type galaxies and SEDs of the 14 galaxies in the ninth neurons are similar to the SB6 galaxies.
            The far right of the network, galaxies with SED comparable to type SB1 and SB2.

            In general, 56 galaxies correspond exactly to K96 types and the other 86 are in between of the initial 12 suggestions.
            As T12 mentioned, part of the reason we could not classify all the galaxies using the K96 model is that the model were constructed from co-adding 12 spectra of the 70 galaxies.
            In this small sample, it is quite possible that the best SEDs do not match any model, perfectly and the original classifications have high uncertainty.

            On the other hand, all the other methods (i.e. $\chi^2$ fitting, trained neural network) of matching SEDs limit themselves to models, and if they could not find the best match, report the results as uncertain ones.
            However, with SOM, galaxies have this freedom to be categorized in the intermediate groups.
            Therefore, if the SED of galaxies do not match completely with any of the model SEDs in Fig.~\ref{fig: k96}, they can be categorized as a SED with similarity to two or more of the groups.

        \subsubsection{1D NETWORKS results and Properties of clustered galaxies}

        In order to check whether our conclusions in Sec.~\ref{sec: 1Dv}~is meaningful and correct, in this section we are going to show the relations between properties of the galaxies in each neuron.

        \begin{figure*}
            \centering
            \includegraphics[width=\textwidth]{../images0.01/1d/props5.png}
            \caption{Comparing the median of four propertied of galaxies in each nod in $1\times2$, $1\times4$, and $1\times8$ networks.}
            \label{fig: props}
        \end{figure*}
